ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-01-19 manuscript.tex
addressed ngspopgen citation

Here we present ANGSD-wrapper, a user-friendly interface to ANGSD. 
ANGSD-wrapper takes the form of a set of configuration files and 'wrapper' scripts (Figure \ref{fig:supp2}) that streamline the execution of multi-step pipelines required for data analysis in ANGSD. 
ANGSD-wrapper also eases the configuration of ANGSD-related programs such as ngsPopGen\jri{please add citation to url for git repo}, ngsF\citep{vieira2013estimating}, and ngsAdmix \citep{pmid24026093}.
Because the large volume of data associated with high throughput sequence analysis is often difficult to visualize, ANGSD-wrapper also provides a suite of interactive visualization tools to plot results and explore patterns at multiple scales.  
We demonstrate some of the analyses possible using ANGSD-wrapper when applied to low-coverage whole-genome data from domesticated maize and two related wild teosinte subspecies. 
ANGSD-wrapper is freely available from \url{https://github.com/mojaveazure/angsd-wrapper}.

>>>>

Here we present ANGSD-wrapper, a user-friendly interface to ANGSD. 
ANGSD-wrapper takes the form of a set of configuration files and 'wrapper' scripts (Figure \ref{fig:supp2}) that streamline the execution of multi-step pipelines required for data analysis in ANGSD. 
ANGSD-wrapper also eases the configuration of ANGSD-related programs such as ngsPopGen \citep{ngsPopGen}, ngsF\citep{vieira2013estimating}, and ngsAdmix \citep{pmid24026093}.
Because the large volume of data associated with high throughput sequence analysis is often difficult to visualize, ANGSD-wrapper also provides a suite of interactive visualization tools to plot results and explore patterns at multiple scales.  
We demonstrate some of the analyses possible using ANGSD-wrapper when applied to low-coverage whole-genome data from domesticated maize and two related wild teosinte subspecies. 
ANGSD-wrapper is freely available from \url{https://github.com/mojaveazure/angsd-wrapper}.
